visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-07-29 manuscript.tex
updated manuscript

  man]{apa7}

@@

\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}

@@

  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}

@@

@@

\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs

@@

  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}

@@

  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}

@@

\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}

@@

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{multigroup confirmatory factor analysis, measurement invariance, visualization, effect size}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports},
  pdfauthor={Erin M. Buchanan1},
  pdflang={en-EN},
  pdfkeywords={multigroup confirmatory factor analysis, measurement invariance, visualization, effect size},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs (Beaujean, 2014). Journals such as \emph{Assessment} regularly publish articles supporting measures of latent constructs wherein a measurement model is established. Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multi-group confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015). With the rise of the replication crisis and ``psychology's renaissance'' (Nelson et al., 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model. This manuscript presents \texttt{visualizemi}, an \emph{R} package that provides functionality to calculate multigroup models, partial invariance, visualizations for (non)-invariance, effect sizes for models and parameters, and potential replication rates compared to random models. Readers will learn how to interpret the impact and size of the proposed non-invariance in models with a focus on potential replication and how to plan for registered reports.
}

@@

Measurement invariance has been explored and implemented for the last fifty years (Jöreskog, 1971; Sörbom, 1978) and implemented in the most popular structural equation modeling programs (Boker et al., 2011; Jöreskog \& Sörbom, 2001; Rosseel, 2012). Byrne et al. (1989) extended the ideas of multi-group testing by suggesting partial invariance (followed by Meredith, 1993). Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same). This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines. As the field pushes back against favoring cutoff criteria and rules of thumb (Marsh et al., 2004; Putnick \& Bornstein, 2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011). This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance (Stark et al., 2006).

@@

Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters. No known visualization techniques have been proposed for measurement invariance. By creating panel visualizations, we can supplement a researcher's ability to judge the strength of the non-invariance differences and effect size for each item. The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance. Within this technique, the individual parameter effect sizes can be calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups. Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful. This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
\item
  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
\item
  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
\item
  Understand the impact of measurement variability on replication and generalizability.
\end{enumerate}

The tutorial will start with simulated data based on known effect sizes using \(d_{MACS}\) and demonstrating the package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level. Last, data from Aiena et al. (2014) examining the measurement invariance of the RS-14 (Wagnild, 2009) will be used to demonstrate the application of the package on real data. The \emph{visualizemi} package vignette includes an additional tutorial walk through.

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{design-and-analysis}{%
\subsection{Design and Analysis}\label{design-and-analysis}}

Data was simulated using the \texttt{simulateData} function in the \emph{R} package \emph{lavaan} (Rosseel, 2012) assuming multivariate normality using a \(\mu\) of 0 and \(\sigma\) of 1 for the data. This function allows you to write \emph{lavaan} syntax for your model with estimated values to generate data for observed variables (see supplemental for examples). The data included two groups of individuals (``Group 1'', ``Group 2'') for a multi-group confirmatory factor analysis (\(n_{group}\) = 250, \emph{N} = 500). The latent variables were assumed to be continuous normal (the package functions do not require this assumption). The model consisted of five observed items predicted by one latent variable (\texttt{lv\ =\textasciitilde{}\ q1\ +\ q2\ +\ q3\ +\ q4\ +\ q5}); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables. Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was simulated.

The Brown (2015) steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with Stark et al. (2006) suggestions, the visualizations show the impact of loadings and intercepts together. A convenience function \texttt{mgcfa} is used for these steps or other measurement invariance test orders and combinations. Fit indices for the steps for multi-group models are presented in the appendix for comparison of cutoff rules of thumb (Cheung \& Rensvold, 2002) to effect sizes and visualizations presented in this manuscript. Fit indices include Akaike Information Criterion (AIC, Akaike, 1998), Bayesian Information Criterion (BIC, Schwarz, 1978), Comparative Fit Index (CFI, Bentler, 1990), Tucker Lewis Index (TLI, Tucker \& Lewis, 1973), root mean squared error of approximation RMSEA (Steiger, 1990), and standardized root mean square residual (SRMR, Bentler, 1995).

\hypertarget{package-code-examples}{%
\section{Package Code Examples}\label{package-code-examples}}

The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}. This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration. The \emph{R} package and replication/effect sizes was added after the original manuscript submission.

\hypertarget{multi-group-cfa-caculation}{%
\subsection{Multi-group CFA Caculation}\label{multi-group-cfa-caculation}}

First, we would create our model code in \emph{lavaan} syntax (Rosseel, 2012). The \texttt{lv} latent variable predicts the five measured variables, which are present as columns in our \texttt{df.invariant} data set. The package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables sometimes provided in manuscripts (rather than the raw data) is provided in the supplemental documentation.

>>>>

  man,floatsintext]{apa7}

@@

\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%

@@

  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}

@@

  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}

@@

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}

@@

\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}

@@

   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}

@@

  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}

@@

\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}

@@

  \usepackage[english]{selnolig} % disable illegal ligatures

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{multigroup confirmatory factor analysis, measurement invariance, visualization, effect size}
\usepackage{lineno}

@@

\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports},
  pdfauthor={Erin M. Buchanan1},
  pdflang={en-EN},
  pdfkeywords={multigroup confirmatory factor analysis, measurement invariance, visualization, effect size},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Latent variable modeling as a lens for psychometric theory is a popular tool for social scientists to examine measurement of constructs (Beaujean, 2014). Journals such as \emph{Assessment} regularly publish articles supporting measures of latent constructs wherein a measurement model is established. Confirmatory factor analysis can be used to investigate the replicability and generalizability of the measurement model in new samples, while multigroup confirmatory factor analysis is used to examine the measurement model across groups within samples (Brown, 2015). With the rise of the replication crisis and ``psychology's renaissance'' (Nelson et al., 2018), interest in divergence in measurement has increased, often focused on small parameter differences within the latent model. This manuscript presents \texttt{visualizemi}, an \emph{R} package that provides functionality to calculate multigroup models, partial invariance, visualizations for (non)-invariance, effect sizes for models and parameters, and potential replication rates compared to random models. Readers will learn how to interpret the impact and size of the proposed non-invariance in models with a focus on potential replication and how to plan for registered reports.
}

@@

Measurement invariance has been explored and implemented for the last fifty years (Jöreskog, 1971; Sörbom, 1978) and implemented in the most popular structural equation modeling programs (Boker et al., 2011; Jöreskog \& Sörbom, 2001; Rosseel, 2012). Byrne et al. (1989) extended the ideas of multigroup testing by suggesting partial invariance (followed by Meredith, 1993). Partial invariance occurs when non-invariance is found but can be attributed to only a few parameter estimate differences between groups (i.e., items 1 and 2 have different factor loadings but all others are the same). This testing provided an advantage to understand where the potential non-invariance may occur for further study and interpretation guidelines. As the field pushes back against favoring cutoff criteria and rules of thumb (Marsh et al., 2004; Putnick \& Bornstein, 2016), an effect size measure for translating ``how much'' non-invariance was developed \(d_{MACS}\) (Nye \& Drasgow, 2011). This effect size examines the differences in observed variables between the two groups for both the factor loading and the item intercept; thus, any differences in either or both will increase the effect size for non-invariance (Stark et al., 2006).

@@

Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multigroup confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters. No known visualization techniques have been proposed for measurement invariance. By creating panel visualizations, we can supplement a researcher's ability to judge the strength of the non-invariance differences and effect size for each item. The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance. Within this technique, the individual parameter effect sizes can be calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups. Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful. This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Learn how to use \emph{visualizemi} to analyze multigroup confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
\item
  Learn how to estimate the potential replication of multigroup models and their parameters using bootstrapping compared to a random group model.
\item
  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
\item
  Understand the impact of measurement variability on replication and generalizability.
\end{enumerate}

The tutorial will start with a general overview of relevant topics to orient readers to invariance testing and MGCFA effect sizes. Next, the reader will learn about the \texttt{visualizemi} package functions for 1) running the multigroup analysis, 2) running a partial invariance analysis, 3) plotting the partial invariance, 4) estimating replication and effect sizes at the model level, and 5) estimating replication and effect sizes at the parameter level. Last, data from Aiena et al. (2014) and Chen et al. (2020) examining the measurement invariance of the RS-14 (Wagnild, 2009) will be used to demonstrate the application of the package on real data. The \emph{visualizemi} package vignette includes an additional tutorial walk through.

\section{Terminology}\label{terminology}

\subsection{MGCFA}\label{mgcfa}

Multigroup confirmatory factor analysis (MGCFA) was proposed as a method to examine differences in scale functioning across groups (Brown, 2015) using structural equation modeling and confirmatory factor analysis (CFA). The goal of MGCFA is to determine if groups are invariant or show the same response patterns on the scale. MGCFA is often performed in sequential steps to determine the location and impact of potential non-invariance. The most common procedure starts by examining overall scale structure for each group individually to show that the groups can be combined into one nested model (i.e., both models at least converge). The combined model, often described as the \emph{configural} model, creates one CFA for both groups that allows each group's estimated parameters to vary. Equality constraints between group parameters are then added sequentially to the model (Brown, 2015). If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.

The first equality constraint added is usually the item factor loadings (\emph{metric} model) which requires items to be related to the latent variable at the same strength across groups. The intercepts are then constrained to be equal across groups (\emph{scalar} model) to determine the invariance of item averages. The item variances (\emph{strict} model) can then be examined to determine if the general variation in item answers are equal across groups. Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations. Non-invariance is determined by examining differences in fit indices between models with constraints versus without (Cheung \& Rensvold, 2002).

\subsection{Partial Invariance}\label{partial-invariance}

If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (Byrne et al., 1989; Meredith, 1993). Similar to \emph{post hoc} follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary. If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant. When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups. The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness. Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.

\subsection{\texorpdfstring{Effect Size: \(d_{MACS}\)}{Effect Size: d\_\{MACS\}}}\label{effect-size-d_macs}

\(d_{MACS}\) was developed from Differential Item Functioning (DIF) measurement in Item Response Theory (IRT, Stark et al., 2004) wherein the effect size (DIF) portrays the group differences that lead to overall item score differences. Item scores can be mathematically defined as:

\[
\hat{X}_{iR} = \tau_{iR} + \lambda_{iR}\xi
\]

\emph{i} indicates an individual item, and \emph{R} indicates the reference group (Nye \& Drasgow, 2011). Therefore, an individual score is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)). Nye and Drasgow (2011) demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\). \(d_{MACS}\) is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for \emph{d} proposed by Cohen (2013). Therefore, if \(\tau\) or \(\lambda\) are individually (or both) different across groups, it will impact all the predicted \(X_{iR}\) scores, and thus, impact \(d_{MACS}\) values. While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance. In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items. Last, in line with general suggestions by Cumming (2012) and Cumming and Calin-Jageman (2016), the visualization of effect sizes in MGCFA would be an added tool for researchers to gauge the size of group differences.

\section{Package Functions}\label{package-functions}

The complete code for this manuscript can be found at \url{https://osf.io/wev5f/}. This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration. The \emph{R} package and replication/effect sizes was added after the original manuscript submission. The simulation study used to design plotting functions and test effect sizes can be found in the supplemental materials, along with worked code examples.

\subsection{\texorpdfstring{MGCFA: \texttt{mgcfa()} Function}{MGCFA: mgcfa() Function}}\label{mgcfa-mgcfa-function}

First, we would create our model code in \emph{lavaan} syntax (Rosseel, 2012). The \emph{visualizemi} package does generally require raw data for bootstrapping purposes, and an example of how to simulate data from models and covariance/correlations tables that sometimes are provided in manuscripts (rather than the raw data) is provided in the supplemental documentation. The \texttt{mgcfa()} function is designed to flexibly allow you to leverage \emph{lavaan}'s package functions to calculate multiple measurement steps at once. You would include:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  the model syntax in the \texttt{model} argument.
\item
  the dataframe in the \texttt{data} argument of our functionl
\item
  the name of the grouping variable in quotes for \texttt{group}.
\item
  and the equality constraints you would like to impose in order in \texttt{group.equal}.
\item
  \texttt{...} any other \emph{lavaan} arguments you would like to use such as \texttt{meanstructure} or \texttt{estimator}.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{model\_coef}: The parameter estimates for each model with the model step included in a \emph{model} column. This set of coefficients can be used for other functions. This dataframe is created with \emph{broom}'s \texttt{tidy()} function if you wish to recreate this table without running the \texttt{mgcfa()} function (Robinson et al., 2023).
\item
  \texttt{model\_fit}: The model fit indices from \texttt{fitmeasures()} to review for overall model fit and invariance judgments. The name of the model is included in a \emph{model} column.
\item
  \texttt{model\_overall}: A saved \emph{lavaan} fitted model of all groups together without any equality constraints or grouping variables. These objects can be used with any function that normally takes a saved model: \texttt{parameterEstimates()}, \texttt{modificationIndices()}, \texttt{semPlot::semPaths()}, and so on (Epskamp, 2022).
\item
  \texttt{group\_models}: A list of saved fitted models for each group separately.
\item
  \texttt{model\_configural}: A saved fitted model for the configural model that nests together each group into one model with no other constraints.
\item
  \texttt{invariance\_models}: A list of saved fitted models that consecutively adds \texttt{group.equal} constraints.
\end{enumerate}

\subsection{\texorpdfstring{Partial Invariance: \texttt{partial\_mi()} Function}{Partial Invariance: partial\_mi() Function}}\label{partial-invariance-partial_mi-function}

The \texttt{partial\_mi()} function aids in the calculation of partial invariance for a specific step of the MGCFA process. The function includes the following arguments:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{saved\_model}: The saved \emph{lavaan} model with the equality constraints at the level of measurement invariance you would like to examine for partial invariance.
\item
  \texttt{data}: The dataframe where the model was estimated.
\item
  \texttt{model}: The model syntax for the overall model.
\item
  \texttt{group}: The grouping variable column in the dataframe.
\item
  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
\item
  \texttt{partial\_step}: The level of partial invariance you wish to test.
\end{enumerate}

In this function, each parameter with the appropriate \emph{lavaan} syntax is relaxed individually (i.e., \texttt{\textasciitilde{}1} for intercepts, \texttt{\textasciitilde{}\textasciitilde{}} for residuals, etc.). The fitted models are saved in the \texttt{models} output, and the \texttt{fit\_table} output includes all fit indices for each model to investigate potential areas of partial invariance based on the researcher's desired criterion.

\subsection{\texorpdfstring{Visualization of Invariance: \texttt{plot\_mi()} Function}{Visualization of Invariance: plot\_mi() Function}}\label{visualization-of-invariance-plot_mi-function}

Once we know which items are non-invariant, the \texttt{model\_coef} output from the \texttt{mgcfa()} can be used directly in \texttt{plot\_mi()}. The plot outputs will be described below. First, here are the arguments for the function:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{data\_coef}: A tidy dataframe of the parameter estimates from the models. This function assumes you have used \texttt{broom::tidy()} on the saved model from \emph{lavaan} and added a column called ``model'' with the name of the model step (Robinson et al., 2023). This function will only run for models that have used the grouping function (i.e., configural, metric, scalar, and strict or other combinations/steps you wish to examine).
\item
  \texttt{model\_step}: Which model do you want to plot? You should match this name to the one you want to extract from your model column in the \texttt{data\_coef}.
\item
  \texttt{item\_name}: Which observed variable from your model syntax do you want to plot? Please list this variable name exactly how it appears in the model.
\item
  \texttt{x\_limits}: What do you want the x-axis limits to be for your invariance plot? The default option is to assume the latent variable is standardized, and therefore, -1 to 1 is recommended. Use only two numbers, a lower and upper limit. This value also constrains the latent mean diagram to help zoom in on group differences because the scale of latent means is usually centered over zero. You can use this parameter to zoom out to a more traditional histogram using \texttt{c(-2,\ 2)}.
\item
  \texttt{y\_limits}: What do you want the y-axis limits to be for your invariance plot? Given that the latent variable is used to predict the observed values in the data, you could use the minimum and maximum values found in the data. If that range is large, consider reducing this value to be able to visualize the results (i.e., otherwise it may be too zoomed out to judge group differences). Use only two numbers, a lower and upper limit.
\item
  \texttt{conf.level}: What confidence limit do you want to plot? Use 1 - \(\alpha\).
\item
  \texttt{model\_results}: In this argument, include the saved \emph{lavaan} output for the model listed in the \texttt{model\_step} argument.
\item
  \texttt{lv\_name}: Include the name of the latent variable, exactly how it is listed in your \emph{lavaan} syntax. You should plot the latent variable that the \texttt{item\_name} is linked to. If you have items that load onto multiple latent variables, you will need to make multiple plots.
\item
  \texttt{plot\_groups}: If you include more than two groups in a multigroup model, the automatic assumption is that you want the first two groups for this visualization. If not, include the names of the groups here to plot.
\end{enumerate}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/invariant-visual.png}}
\caption{\label{fig:invariant-pic}Invariant model visualization demonstrating the components of the \texttt{plot\_mi()} function in \emph{visualizemi}.}
\end{figure}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \texttt{intercept}: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings. Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)). The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data this simulated item. The ribbon bands around the plotted slopes indicate the confidence interval for that estimate. In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
\end{enumerate}

The item intercepts (\(b_0\)) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero. These are represented by a dot with a set of confidence error bars around the point. In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different. You can use \texttt{y\_limits} to zoom in on the graph if these are too small to be distinguishable.
3) \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data. The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on. The lines indicate the means of the latent variables from the simulated dataset. Group labels are represented in the figure caption on the bottom. Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
4) \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item. Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\). It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate. Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot. The black bars represent the estimated residual for each group. The distributions are plotted to represent the normal spread of values using the standard error of the residuals. The violin plot allows for direct comparison of those residuals and their potential distributions. Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value. The plots are included separately so they can be arranged in a different fashion if desired.

\subsection{\texorpdfstring{Model Replication and Effect Sizes: \texttt{bootstrap\_model()} Function}{Model Replication and Effect Sizes: bootstrap\_model() Function}}\label{model-replication-and-effect-sizes-bootstrap_model-function}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints. This model should include all other lavaan settings you would like to use, such as estimator or ordered.
\item
  \texttt{data}: The dataframe where the model was estimated.
\item
  \texttt{model}: The model syntax for the overall model.
\item
  \texttt{group}: The grouping variable column in the dataframe.
\item
  \texttt{nboot}: The number of bootstraps to run.
\item
  \texttt{invariance\_index}: The fit index you would like to use to determine invariance. Please use options and labeling from \emph{lavaan} - see \texttt{fitmeasures()} for options.
\item
  \texttt{invariance\_rule}: The invariance difference score you would like to use as your rule.
\item
  \texttt{group.equal}: The equality constraints including in your original multigroup tests.
\end{enumerate}

\subsection{\texorpdfstring{Parameter Replication and Effect Sizes: \texttt{bootstrap\_partial()} Function}{Parameter Replication and Effect Sizes: bootstrap\_partial() Function}}\label{parameter-replication-and-effect-sizes-bootstrap_partial-function}

After examining the overall model potential replication effect size, the individual parameters within a model can be bootstrapped for partial invariance to with that parameter relaxed (overall partial model statistics) and the difference in group parameter estimates (parameter effect size). This function uses arguments seen in other functions, so they will not be repeated here. The general setup consists of using the model you think could be partially invariant in the \texttt{saved\_model} argument and the fit index for comparison for the model with less constraints in \texttt{invariance\_compare}. The \texttt{partial\_step} argument will be used to determine which operation syntax (i.e.~\texttt{=\textasciitilde{}} for loadings) to relax for modeling.

Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results from separated by bootstrapping versus random and invariant/non-invariant. The \(d_s\) for between groups Cohen's \(d\) is included. Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs. This dataframe should be used to determine which parameter may be different and at what size between groups in a replication of the study. The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.

Plots of the results from dataframes can be found within the \texttt{bootstrap\_partial()} function. Figure \ref{fig:invariance-partial-fig} shows the difference between parameters for groups in the bootstrapped and randomly assigned group runs in simulated data. Figure \ref{fig:density-partial-fig} shows the density plot of the estimates for each group organized by bootstrapped and randomly assigned groups and the invariance decision for each bootstrapped run. Last, Figure \ref{fig:effect-partial-fig} indicates the \(d_s\) value between groups with an indication of the number of data points in each estimate (i.e., dot size). These visualizations should allow a researcher to understand the likelihood of replication for each parameter, as well as the potential size of the differences. Therefore, one could indicate a specific smallest effect size of interest, rather than a invariance cut-off rule of thumb when planning a replication or registered report.

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-invariance.png}}
\caption{\label{fig:invariance-partial-fig}Visualization of the difference score between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data.}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-density.png}}
\caption{\label{fig:density-partial-fig}Visualization of the number of estimates for each group by bootstrapped and randomly assigned group runs by their invariance decision.}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/boot-partial-effects.png}}
\caption{\label{fig:effect-partial-fig}Visualization of effect size between groups by parameter for invariant and non-invariant bootstrapped and randomly assigned group data. The size of the dots indicate the number of data points for that estimate.}
\end{figure}

\section{An Example Analysis}\label{an-example-analysis}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs7-img-1.pdf}}
\caption{\label{fig:rs7-img}RS7 Item Invariance Visualization}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/rs6-img-1.pdf}}
\caption{\label{fig:rs6-img}RS6 Item Invariance Visualization}
\end{figure}
